\section{Generating allow and downtaudit rules}

Now we generate \texttt{allow} and \texttt{donataudit} rules for our
\emph{Libre Office} policy (page \pageref{creating_new_policy}).

Switch your \emph{SELinux} to \emph{Permissive} mode:
\texttt{setenforce 0}, and run \texttt{/usr/bin/libreoffice}. You will
receive many alerts in \emph{UDDTray}. Type \texttt{libre\_office} in a
\emph{Filter} field of alerts tab {[}1{]}. Select all chosen alerts
{[}2{]}, or type for it \emph{Ctrl+A}. Press \emph{Append to editor}
button {[}3{]}, and activate \emph{Generate policy} button. When
\emph{Generate policy} was unchecked you could see allow rules in
\emph{SELinux policy} tab {[}5{]}.


\illustrationWithCaption[0.85]{filter_num}{Generating allow rules}

Append generated rules in \texttt{libre\_office.te} files. If you don't
want to grant some permission for \emph{Libre Office} and want to ignore
received messages replace keyword \texttt{allow} with
\texttt{dontaudit}.

Append \texttt{allow} and \texttt{dontaudit} rules for
\texttt{libre\_office\_secret\_t} domain (run
\texttt{/usr/bin/libreoffice\_secret}) in the same way. Then rebuild and
install policy.

After installation you can try to switch \emph{SELinux} in
\emph{Enforcing} mode. Type \texttt{setenforce 1} in a root console.
When you run \emph{Libre Office} again you will receive new alerts.
Append rules for it too.

\textbf{Warning!} Some alerts are not shown at the alerts tab, because
there are not system. You could try to generate policy for it using
\emph{Generate policy for /var/log/messages} function. Other alerts are
not shown because there are \texttt{dontaudit} rules for it in other
policies. If you want to see alerts for \texttt{dontaudit} rules rebuild
your policy: \texttt{semodule -D}. If you want hide these events type
\texttt{semodule -DB} in your root console.
